---
title: Final datatests for regional pocketbooks
author: Markus Kainu
date: "Last updated: ``r Sys.time()``"
output: 
  html_document:
    theme: yeti 
    toc: true
    toc_float: true
    code_folding: hide
---
  

```{r setup, knitr_setup, include=F}
library(knitr)
knitr::opts_chunk$set(list(echo=TRUE,
                           eval=TRUE,
                           cache=FALSE,
                           warning=FALSE,
                           message=FALSE, 
                           cache.path="~/Lataukset"))
opts_chunk$set(fig.width = 10, fig.height = 10)
options(scipen=999)
#+ setup, include=FALSE
library(stringr)
library(tidyverse)
library(extrafont)
loadfonts()
library(svglite)
library(showtext)
library(hrbrthemes)

dir.create("~/Lataukset/wb", recursive = TRUE, showWarnings = FALSE)

pull_unzip_fao <- function(url="http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Land_E_All_Data_(Normalized).zip") {
  filename <- gsub("^.+/","",url)
  if (!file.exists(paste0("~/Lataukset/",filename))) {
    download.file(url, destfile=paste0("~/Lataukset/",filename))
    unzip(paste0("~/Lataukset/",filename), exdir = "~/Lataukset/")
  }
  if (grepl("\\(Norm\\)",filename)) filename <- gsub("_\\(Norm\\)","",filename) 
  d <- read_csv(gsub(".zip",".csv", paste0("~/Lataukset/",filename)))
  return(d)
}

# pull_unzip_wb <- function(url="http://api.worldbank.org/v2/en/indicator/ER.LND.PTLD.ZS?downloadformat=csv") {
#   unlink("~/Lataukset/wb", recursive = TRUE, force=TRUE)
#   dir.create("~/Lataukset/wb", showWarnings = FALSE)
#   download.file(url, destfile="~/Lataukset/wb/wb.zip", method = "wget")
#   flies <- list.files("~/Lataukset/wb")[!grepl("Metadata|zip",list.files("~/Lataukset/wb"))]
#   d <- read_csv(paste0("~/Lataukset/wb/",flies))
#   return(d)
# }



```

# Charts

```{r cars, eval=FALSE}
geogr = function(x, n = 1){
  T = length(x)
  if(sum(is.na(x)) == T){
    geogr = rep(NA, T)
    warning("All values are NA")
  } else {
    firstObs = ifelse(any(is.na(x)), min(which(!is.na(x))), 1)
    if(n > T - firstObs - 1){
      geogr = rep(NA, T)
      warning("Time series does not have sufficient values")
    } else {
      geogr = double(T)
      geogr[1:(firstObs + n - 1)] = NA
      geogr[(firstObs + n):T] = ((x[(firstObs + n):T]/
                                    x[firstObs:(T - n)])^(1/n) - 1) * 100 
    }
  }
  geogr
}


x <- c(83373,84878,85616,85474,84419,82326,79316,75902,72786,70473)
x <- c(6197,6692,7250,7863,8526,9235,9987,10781,11616,12494,13414,14376,15376,16410,17470,18551,19646,20755,21888,23061,24279,25560,26892,28231,29514,30706,31781,32769,33746,34819,36063,37502,39112,40862,42704,44597,46515,48458,50431,52449,54511,56674,58904,61003,62707,63854,64291,64147,63888,64161,65399,67770,71046,74783,78337,81223,83373,84878,85616,85474,84419,82326,79316,75902,72786,70473)
gr <- geogr(x, n=10)
mean(gr[57:66])



mean(c(2.63,2.84,2.97,2.91,2.59,1.96,1.11,0.15,-0.73,-1.41,-1.85))
```



<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->

# Country profiles




## 1. The following variables appear to have some sort of systemic error:

### a) Area equipped for irrigation (1 ha) 

>2015 column is NA for all countries but there is data available from 2012. I checked this against the Water Tables file that Markus sent me.

**Check**

- meta: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L79>
- used as is
- in book:
    - India: 49500,60432,70400
    - Philippines: 1550,1361,1708
    - Serbia: NA,NA,78
    - Italy: 3858,3856,4004
    - Jordan: 63,77,105
    - Egypt: 2648,3291,3670
    - Uganda: 9,9,11
    - Ethiopia: 290,290,800

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries</p>
</div>

**FAOSTAT data**

```{r}
d <- pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Land_E_All_Data_(Normalized).zip")
d %>% 
  filter(`Area Code` %in% c(100,171,112,59,272,106,226,59,238), 
         Year >= 1988, 
         `Element Code` == 5110,
         `Item Code` == 6690
         ) %>% 
  na.omit() %>%
  select(Area,Year,Value) %>% 
  spread(., key = Year, value = Value) %>% 
  kable()

```


### b. Fertilizers, Nitrogen (kg per ha) 

>There appears to be an issue with the values in the year 2000. Of the eight countries I checked, the value for 2000 was correct in  4 countries and wrong in 4 countries.

**Check**

- meta: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L109>
- constructed: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Construction2015.csv#L109> 
    - <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L108> / 
- in book:
    - India: NA,65,100
    - Philippines: NA,59,63
    - Serbia: NA,NA,90.8
    - Italy: NA,80.4,65.8
    - Jordan: NA,214,88
    - Egypt: NA,469,350
    - Uganda: NA,1,1
    - Ethiopia: NA,3,15
    - Bangladesh: NA 109 145
    - Senegal: NA 4 6
    - Egypt: NA 469 350
    - Algeria: NA 2 32



<!-- <div class="alert alert-dismissible alert-success"> -->
<!--   <button type="button" class="close" data-dismiss="alert">&times;</button> -->
<!--   <p>Match for selected countries</p> -->
<!-- </div> -->

**FAOSTAT data**

```{r}
pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Fertilizers_E_All_Data_(Normalized).zip")  %>% 
  filter(
    # CountryCode %in% c(100,171,112,59,272,106,226,59,238), 
    `Area Code` %in% c(16,195,4,59,230,
                        100,171,112,272,106,226,238), 
    Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 5155,
    # ItemCode == 3102
    `Item Code` == 3102
         ) %>% 
  na.omit() %>%
  select(Area,Year,Value) %>% 
  rename(nitro = Value) -> da

pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Land_E_All_Data_(Normalized).zip") %>% 
  filter(
    # CountryCode %in% c(100,171,112,59,272,106,226,59,238), 
    `Area Code` %in% c(16,195,4,59,230,
                       100,171,112,272,106,226,238), 
    Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 5110,
    # ItemCode == 3102
    `Item Code` == 6620
         ) %>% 
  na.omit() %>%
  select(Area,Year,Value)  %>% 
  rename(area = Value) -> db
  
  left_join(db,da) %>% 
    mutate(share = nitro/area) %>% 
    gather(., key = var, value = val, 3:5) %>% 
    spread(., key = Year, value = val) %>% 
    kable(digits = 1)
```


### c. Fertilizers, Phosphate (kg per ha) 

>There appears to be an issue with the values in the year 2000. Of the eight countries I checked, the value for 2000 was correct in  3 countries and wrong in 5 countries.

**Check**

- meta: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L109>
- constructed: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Construction2015.csv#L109> 
    - <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L108> / 
- in book:
    - India: NA,24,38
    - Philippines: NA,21,16
    - Serbia: NA,NA,23.7
    - Italy: NA,30,18.7
    - Jordan: NA,402,0
    - Egypt: NA,52,108
    - Uganda: NA,0,0
    - Ethiopia: NA,2,10
    - Senegal: NA 4 0
    - Algeria: NA 1 9
    - Egypt: NA 52 108
    - Bangladesh: NA 23 66

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries</p>
</div>
    

**FAOSTAT data**

```{r}
pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Fertilizers_E_All_Data_(Normalized).zip")  %>% 
  filter(
    # CountryCode %in% c(100,171,112,59,272,106,226,59,238), 
    `Area Code` %in% c(16,195,4,59,230,
                       100,171,112,272,106,226,238), 
    Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 5155,
    # ItemCode == 3102
    `Item Code` == 3103
         ) %>% 
  na.omit() %>%
  select(Area,Year,Value) %>% 
  rename(phos = Value) -> da

pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Inputs_Land_E_All_Data_(Normalized).zip") %>% 
  filter(
    # CountryCode %in% c(100,171,112,59,272,106,226,59,238), 
    `Area Code` %in% c(16,195,4,59,230,
                       100,171,112,272,106,226,238), 
    Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 5110,
    # ItemCode == 3102
    `Item Code` == 6620
         ) %>% 
  na.omit() %>%
  select(Area,Year,Value)  %>% 
  rename(area = Value) -> db
  
  left_join(db,da) %>% 
    mutate(share = phos/area) %>% 
    gather(., key = var, value = val, 3:5) %>% 
    spread(., key = Year, value = val) %>% 
    kable(digits = 1)
```



### d. Terrestrial protect areas (% total land area)

>Data is correct and incorrect for countries/years seemingly without reason. There are enough incorrect values I would take a look.

- data: <http://data.worldbank.org/indicator/ER.LND.PTLD.ZS>
- in book:
    - India: 4.7,5,5.3
    - Philippines: 8.7,10.8,11
    - Serbia: NA,NA,6.8
    - Italy: 5.8,17.4,21.5
    - Jordan: 1.1,1.9,2.1
    - Egypt: 0.4,4.3,11.2
    - Uganda: 12.3,12.9,16
    - Ethiopia: 17.7,17.7,18.4

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries, but early Serbia. This is due to how the country codes from non-FAOSTAT data are treated for ex-Jugoslavian countries. We would need to have good reasons to unwind that process..</p>
</div>

**World Bank data**

```{r}
library(WDI)
WDI(country = c("IN","PH","RS","IT","JO","EG","UG","ET"), indicator = "ER.LND.PTLD.ZS", start = 1988, end = 2016) %>% 
  select(-iso2c) %>% 
  spread(., key = year, value = ER.LND.PTLD.ZS) %>% 
  kable()
```


### e. Net GHG emissions from AFOLU (CO2 eq, Mt)

>Data is correct and incorrect for countries/years seemingly without reason. There are enough incorrect values I would take a look.

- computed as <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/run.R#L1023>
- which is <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L605> + <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/Metadata2015.csv#L617>
- in book:
    - India: 456,505,749
    - Philippines: 36,44,-7
    - Serbia: NA,NA,5
    - Italy: 5,0,-4
    - Jordan: 1,1,1
    - Egypt: 19,26,31
    - Uganda: 31,34,50
    - Ethiopia: 82,86,115
    - Australia: 163 196 75
    - Algeria: 8 9 12
    - Rwanda: 11 11 4
    - Ukraine: 23 -10 28
    - Slovakia: -6 -7 -3

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries</p>
</div>

**FAOSTAT data**

```{r}
# 7231 	1711 +
# 7217 	1707 

# pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Emissions_Land_Use_Land_Use_Total_E_All_Data_(Norm).zip")
# 
# pull_unzip_fao("http://fenixservices.fao.org/faostat/static/bulkdownloads/Emissions_Agriculture_Agriculture_total_E_All_Data_(Norm).zip")

read_csv("~/Lataukset/Emissions_Agriculture_Agriculture_total_E_All_Data_(Norm).csv") %>% 
  filter(
    `Country Code` %in% c(4,10,184,230,199,
      100,171,112,59,272,106,226,59,238),
    # `Area Code` %in% c(100,171,112,59,272,106,226,59,238), 
    # Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 7231,
    # ItemCode == 3102
    `Item Code` == 1711
         ) %>% 
  na.omit() %>%
  select(Country,Year,Value) %>% 
  rename(total_agr = Value) -> da

read_csv("~/Lataukset/Emissions_Land_Use_Land_Use_Total_E_All_Data_(Norm).csv") %>% 
  filter(
    `Country Code` %in% c(4,10,184,230,199,
                          100,171,112,59,272,106,226,59,238),
    # `Area Code` %in% c(100,171,112,59,272,106,226,59,238), 
    # Year >= 1988, 
    # ElementCode == 5155,
    `Element Code` == 7217,
    # ItemCode == 3102
    `Item Code` == 1707
         ) %>% 
  na.omit() %>%
  select(Country,Year,Value) %>% 
  rename(land_use = Value) -> db
  
left_join(db,da) %>% 
    mutate(AFOLU = total_agr + land_use) %>% 
    gather(., key = var, value = val, 3:5) %>% 
    spread(., key = Year, value = val) %>% 
    kable(digits = 1)

```


<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->

## There are still a few data points I have not been able to find; therefore the data still has not been checked on the following items:

### a. Population, rural (% total population) 

>REU book disaggregates M/F and I cannot find the data disaggregated. This variable in the other books is correct (and not disaggregated)

This is one of the many custom indicators for REU

- raw data is processed here: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/code/manualdata_scripts/overweight2015.R#L45> from this data: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/raw/rur_rub_pocketbook_data.csv> originally from [Urban and Rural Population by Age and Sex, 1980-2015](http://www.un.org/en/development/desa/population/publications/dataset/urban/urbanAndRuralPopulationByAgeAndSex.shtml) exactly [this excel](http://www.un.org/en/development/desa/population/publications/dataset/urban/URPAS_2014_ALL.xlsx)
- actual indicator is combined: <https://github.com/UNFAOstatistics/pocketbook/blob/master/input/code/code_countryprofiles.R#L279> 


in the book:

- Serbia: NA, NA, 22.3/22.1
- Italy: 16.5/16.8, 16.2/16.6, 15.4/15.6
- Finland: 10.3/10.3, 9/8.9, 7.9/7.8

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match!</p>
</div>

**In UN Pop data**

```{r}
if (!file.exists("~/Lataukset/URPAS_2014_ALL.xlsx")){
  download.file("http://www.un.org/en/development/desa/population/publications/dataset/urban/URPAS_2014_ALL.xlsx", destfile = "~/Lataukset/URPAS_2014_ALL.xlsx")
}
d <- readxl::read_excel("~/Lataukset/URPAS_2014_ALL.xlsx")
  
d %>% filter(LocationName %in% c("Serbia","Italy","Finland")) %>% 
  select(LocationName,Year,Sex,AreaType,Total) %>%
  spread(., key = AreaType, value = Total) %>% 
  group_by(LocationName,Year) %>% 
  mutate(tot_pop = sum(Total)) %>% 
  ungroup() %>% 
  select(-Total,-Urban) %>% 
  spread(., key = Sex, value = Rural) %>% 
  mutate(male = Male/tot_pop*100,
         female = Female/tot_pop*100) %>% 
  select(-tot_pop,-Female,-Male) %>% 
  gather(., key = sex, value = share, 3:4) %>% 
  spread(., key=Year, value = share) %>% 
  knitr::kable(digits = 1)
```


### b. Overweight, adults (m/f, %)

**This indicator was re-computed as the source data had changed! Data now less sparse ie. less NA in tables**

- data is pulled here: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/code/manualdata_scripts/overweight2015.R#L9> from <http://apps.who.int/gho/athena/data/data-coded.csv?target=GHO/NCD_BMI_25A&filter=AGEGROUP:*;COUNTRY:*;SEX:*>

- Serbia: NA, NA, 59.3/45.6
- Italy: 53/42.4, 59/47, 65.7/53.2
- Finland: 50.1/38.8, 56.1/44, 62/48.6

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries, but early Serbia. This is due to how the country codes from non-FAOSTAT data are treated for ex-Jugoslavian countries. We would need to have good reasons to unwind that process..</p>
</div>

```{r}
d <- read.csv("http://apps.who.int/gho/athena/data/data-coded.csv?target=GHO/NCD_BMI_25A&filter=AGEGROUP:*;COUNTRY:*;SEX:*")
d %>% 
  as_tibble() %>% 
  select(COUNTRY,YEAR,SEX,Numeric) %>% 
  spread(., key = SEX, value = Numeric) %>% 
  filter(YEAR >= 1989, COUNTRY %in% c("FIN","ITA","SRB")) %>% 
  gather(., key = sex, value = val, 3:4) %>% 
  spread(., key=YEAR,value = val) %>% 
  knitr::kable(digits = 1)
```



### c. Obesity, adults (m/f, %)

**This indicator was re-computed as the source data had changed! Data now less sparse ie. less NA in tables**


- data is pulled in here: <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/code/manualdata_scripts/overweight2015.R#L22> from <http://apps.who.int/gho/athena/data/data-coded.csv?target=GHO/NCD_BMI_30A&filter=AGEGROUP:*;COUNTRY:*;SEX:*>


- Serbia: NA, NA, 17.6/18
- Italy: 11.2/14.3, 15.1/17.3, 21.4/21.6
- Finland: 11.8/11.9, 15.8/15.5, 21.4/19.9

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Match for selected countries, but early Serbia. This is due to how the country codes from non-FAOSTAT data are treated for ex-Jugoslavian countries. We would need to have good reasons to unwind that process..</p>
</div>

```{r}
d <- read.csv("http://apps.who.int/gho/athena/data/data-coded.csv?target=GHO/NCD_BMI_30A&filter=AGEGROUP:*;COUNTRY:*;SEX:*")  
d %>% 
  as_tibble() %>% 
  select(COUNTRY,YEAR,SEX,Numeric) %>% 
  spread(., key = SEX, value = Numeric) %>% 
  filter(COUNTRY %in% c("FIN","ITA","SRB")) %>%
  gather(., key = sex, value = val, 3:4) %>% 
  spread(., key=YEAR,value = val) %>% 
  knitr::kable(digits = 1)


```



### d. Fish, Production Index (Could not find in FISHSTAT)

Data is this from Fisheries <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/raw/fishery2015/Fisheries_bycountry_1990-2013.xlsx>



### e. Fish, Net Trade (Could not find in FISHSTAT)

Data is this from Fisheries <https://github.com/UNFAOstatistics/pocketbook_database/blob/master/input_data/raw/fishery2015/Trade1990_2012_ESSJun2015.xlsx>



<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->

## The following indicators are pulling correct data, but we should update the Label


### a. Water resources (m3/person/year) 

>this is Renewable Water Resources (currently this is listed in definition but if we can fit it in on the profile page I think it would be better)

<div class="alert alert-dismissible alert-success">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>Fixed now as `Renewable water resources (m3/person/year)`</p>
</div>


### b. Health expenditure per capita, PPP ($) 

>This indicator is only in REU book. I checked against WB “Health expenditure per capita PPP constant 2011 international \$” and it did not match. However, it did match when checked against WB “Health expenditure per capita (current US$).” So we just need to update the label from PPP to current US \$ and it should be fine.

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>we may also change it into *international* if that would be better for over time comparisons?</p>
</div>


## Data corrent, but labels different 

>The following three indicators all seem to be the same variable, pulling the same correct data, but with different labels. Each country profile has 2 of the following 3 duplicated indicators. We should choose one (presumably the one that already is in all the books), and remove the others.

### a. Water withdrawal by agriculture (% of total) – appears in RNE, RAP, RAF

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not harmonise yet!!</p>
</div>


### b. Renewable water res withdrawn (% of total) – appears in ALL books

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not harmonise yet!!</p>
</div>


### c. Share of renewable water resources (%) - appears in REU only

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not harmonise yet!!</p>
</div>


<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->

## Data correct, but sparse, lots of NA's

>The following three indicators are pulling correctly, but there is very little data overall so they appear as NA in almost every country. They should be removed and replaced (not necessarily for this round of books, but definitely in future books).

### a. Share of food expenditure (%)


<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not remove yet!</p>
</div>


### b. Vitamin A deficiency, total pop (%)

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not remove yet!</p>
</div>


### c. Iodine deficiency, children aged 6 to 12 (%)

<div class="alert alert-dismissible alert-info">
  <button type="button" class="close" data-dismiss="alert">&times;</button>
  <p>I agree, but did not remove yet!</p>
</div>


<!-- ---------------------------------------------------------------------- -->
<!-- ---------------------------------------------------------------------- -->

# Help functions etc.

```{r}
readr::read_csv("~/faosync/pocketbooks/pocketbook/input/data/FAOcountryProfile.csv") %>% distinct(FAOST_CODE,FAO_TABLE_NAME) %>% 
  DT::datatable()
```


# sessioninfo()
```{r sessioninfo, knitr_setup, include=F}
sessionInfo()
```